Language-Based Security for Low-Level MPC

### 2024-09-03 ppdp24/slides.tex
checkpoint

  \begin{exampleblock}{Example: 3-Party $\fplus$ in $\mathbb{F}_2$ (where $\fplus$ is $\exor$ and $\ftimes$ is $\wedge$)}
  $$
  \idealf(\sx{1}{1},\sx{2}{2},\sx{3}{3}) =
  \sx{1}{1}\ \fplus\ \sx{2}{2}\ \fplus\ \sx{3}{3}
  $$
  Suppose in a run of $\prog$ the output of $\prog$ is 1 and $C = \{ 3 \}$ and
  the adversary knows $\sx{3}{3} = 0$.
  Therefore the adversary knows that either:
  $$
  \sx{1}{1} = 0 \text{\ and\ } \sx{2}{2} = 1
  $$
  or:
  $$
  \sx{1}{1} = 1 \text{\ and\ } \sx{2}{2} = 0
  $$
  with equal probability of .5. \cemph{Adversarial views from the run of $\prog$ should not
    allow the adversary better guesses.}
  \end{exampleblock}

@@

  \begin{exampleblock}{Example: 2-Party GMW in $\mathbb{F}_2$}
    Rep.~invariant: each client in $\setit{1,2}$ holds a share of wire values.
    \begin{itemize}
    \item $\ttt{andgmw}(x,y,z)$:
      \begin{itemize}
      \item Input shares $\mx{x}{1}$, $\mx{x}{2}$ and $\mx{y}{1}$, $\mx{y}{2}$--
        wire value for $x$ is $\mx{x}{1} + \mx{x}{2}$, etc.
      \item Output shares $\mx{z}{1}$, $\mx{z}{2}$ received during gate execution.
        $$
        \mx{z}{1} + \mx{z}{2} = (\mx{x}{1} + \mx{x}{2}) * (\mx{y}{1} + \mx{y}{2})
        $$
      \end{itemize}
    \end{itemize}    
  \end{exampleblock}

@@

  \begin{exampleblock}{2-Party GMW (Contd.)}
    \begin{itemize}
    \item $\ttt{andgmw}(x,y,z)$:
      \begin{itemize}
      \item Picking dummy for $x,y,z$, we can automatically generate a
        generic ``and'' gate $\prog_{\wedge}$ in Overture
      \item Automatically calculate the pmf of $\prog_{\wedge}$.
      \item Pmf can be queried to verify critical properties-- e.g., the
        uniform distribution of output shares under any input conditions. 
      \end{itemize}
      Once properties of gates are verified, we can show that rep.~invariants
      are maintained in any circuit.
      \begin{itemize}
      \item Leverage logics for reasoning about probabilistic programming: Probabilistic
        Separation Logic, Lilac.
      \item Manual proofs, but automated tactics and applicability to any circuit.
      \end{itemize}
    \end{itemize}

>>>>

  \begin{exampleblock}{Example: 3-Party $\fplus$ in $\mathbb{F}_2$ (where $\fplus$ is $\exor$ and $\ftimes$ is $\wedge$)}
  $$
  \idealf(\sx{1}{1},\sx{2}{2},\sx{3}{3}) =
  \sx{1}{1}\ \fplus\ \sx{2}{2}\ \fplus\ \sx{3}{3}
  $$
  Suppose in a run of $\prog$ the output of $\prog$ is 1 and $C = \{ 3 \}$ and
  the adversary knows $\sx{3}{3} = 0$.
  Therefore the adversary knows that either:
  $$
  \sx{1}{1} = 0 \text{\ and\ } \sx{2}{2} = 1
  $$
  or:
  $$
  \sx{1}{1} = 1 \text{\ and\ } \sx{2}{2} = 0
  $$
  with equal joint probability of .5. \cemph{Adversarial views from the run of $\prog$ should not
    allow the adversary better guesses.}
  \end{exampleblock}

@@

  \begin{exampleblock}{Example: 2-Party GMW in $\mathbb{F}_2$}
    Rep.~invariant: each client in $\setit{1,2}$ holds a share of wire values.

    $\ttt{andgmw}(x,y,z)$:

    \begin{itemize}
    \item Input shares $\mx{x}{1}$, $\mx{x}{2}$ and $\mx{y}{1}$, $\mx{y}{2}$--
      wire value for $x$ is $\mx{x}{1} + \mx{x}{2}$, etc.
    \item Output shares $\mx{z}{1}$, $\mx{z}{2}$ received during gate execution.
      $$
      \mx{z}{1} + \mx{z}{2} = (\mx{x}{1} + \mx{x}{2}) * (\mx{y}{1} + \mx{y}{2})
      $$
    \end{itemize}

@@

  \begin{exampleblock}{2-Party GMW (Contd.)}

    Picking dummy $x,y,z$, we can execute $\ttt{andgmw}(x,y,z)$
    to generate a generic ``and'' gate $\prog_{\wedge}$ in Overture.
    \begin{itemize}
    \item Automatically calculate the pmf of $\prog_{\wedge}$.
    \item Pmf can be queried to verify critical properties-- e.g., the
      uniform distribution of output shares under any input conditions. 
    \end{itemize}
    Once properties of gates are verified, we can prove that rep.~invariants
    are maintained in any circuit.
    \begin{itemize}
    \item Manual proofs, but automated tactics and applicability to any circuit.
    \item Leverage logics for reasoning about probabilistic programming: Probabilistic
      Separation Logic, Lilac.
    \end{itemize}
